Road Segment Prioritization for Bicycle Infrastructure

### 2020-11-06 README.Rmd
paper: alg writeup + code cleaning

- Community Detection
- Other Cities

@@

The results show that Manchester can be split into three large communities and one small one (Figure \@ref(fig:communitiesmanchester)).

@@

Algorithm 2: Egalitarian Growth (Focus on Fair Distribution of Resources)

@@

```{r growthtotal, fig.cap="Comparing Overall Person-Km Satisfied (Manchester)", out.width="45%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_existing_infra_satisfied_km_all_flow_column.png",
  "data/Manchester/Plots/Growth_Results/growth_community_4_satisfied_km_all_flow_column.png"
))
```

```{r growthcommunities, fig.cap="Comparing Community Level Person-Km Satisfied (Manchester)", out.width="45%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_existing_infra_satisfied_km_community_flow_column.png",
  "data/Manchester/Plots/Growth_Results/growth_community_4_satisfied_km_community_flow_column.png"
))
```

```{r growth3MapandBar, fig.cap="Results of Alg. 2 (Manchester)", out.width="45%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_community_4_priority_all_FLOW.png",
  "data/Manchester/Plots/Growth_Results/growth_community_4_investment_highways_flow.png"
))
```

@@

Existing cycling infrastructure is made up of many disconnected components. Both Algorithm 1 and 2 start with all existing segregated cycling infrastructure and aim to create an efficient, connected network. Figure \@ref(fig:componentsandGCC) compares the performance of both Algorithms in terms of connectivity gains. We can see that, for all three cities analyzed, the number of components is gradually reduced as more infrastructure is added (this is true for both Algorithms). However these connectivity gains require considerable investment; both algorithms take almost 150km of investment to reduce the number of components by half.

Consistent growth can also be seen for the size of the Largest Connected Component in the proposed bicycle network (Figure \@ref(fig:componentsandGCC)). Again, we can see from the results of the three different cities that there is little difference between both Algorithms.

```{r componentsandGCC, fig.cap="Network Characteristics", out.width="45%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_existing_infra_components_number_comparisonManchester.png",
  "data/Manchester/Plots/Growth_Results/growth_existing_infra_components_gcc_comparisonManchester.png"
))
```

>>>>

- Lit Review: I can also organize this thematically and trim down **Planning Cycling Networks** substantially. I would then add some literature in:
  - Calculating Potential Demand
  - Routing
  - Road Segment Prioritization
- Community Detection: Where in the document should this section be?
- Other Cities

@@

The results show that Manchester can be split into four large communities and one small one (Figure \@ref(fig:communitiesmanchester)).

@@

## Algorithm 2: Egalitarian Growth (Focus on Fair Distribution of Resources)

@@

The results of the community detection are used to evaluate the algorithms. This is done by looking at the *person-km satisfied* as cycling infrastructure is added. Person-km is a measure of the total km cycled on a road segment, so it is the product of the number of potential commuters cycling on that road segment ($flow$) and the length of the segment in km ($l$). For each road segment, the person-km is equal to $flow * l$. In the case of Manchester, Table (**Reference the table**) shows that almost half of the person-km is in community 1 , while only 0.5\% of total person-km on the network is in community 5.

```{r personkmtable, echo=FALSE, message = FALSE}

library(tidyverse)
library(sf)

table <- readRDS("data/Manchester/graph_with_flows_weighted_communities.RDS")
# we weigh the flow on each edge by its distance. We can then get how much of the commuter km are satisfied
table$person_km <- table$flow * table$d
# get % of total person km on each link
table$person_km_perc <- (table$person_km / sum(table$person_km)) * 100

table <- table %>% sf::st_drop_geometry() %>% 
  dplyr::group_by(Community) %>%
  summarize(`Person-Km (Total)` = round(sum(person_km),0),
            `Person-Km (%)` = round(sum(person_km_perc),1))

knitr::kable(table,
             caption = "Total Person-Km in Different Communities (Manchester)")

```

Looking at the person-km satisfied (Figure \@ref(fig:growthtotal)), we see that the incremental addition of cycling infrastructure is better distributed between communities using Algorithm 2; equal distribution of investment results in the gain in % of person km satisfied in each community being inversely correlated with the size of the community. In addition, we find that the restrictions imposed by Algorithm 2 on the network growth do not seem to have a noticeable effect on the city-wide \% of person-km satisfied. Comparing both algorithms, we can see that Algorithm 1 provides only marginally quicker city-wide gains than Algorithm 2.

```{r growthtotal, fig.cap="Comparing Overall (Dashed) and Community Level Person-Km Satisfied (Manchester)", out.width="45%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_utilitarian_satisfied_km_both_flow_column.png",
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_satisfied_km_both_flow_column.png"
))
```

Figure \@ref(fig:growth3MapandBar) gives us a geographic representation of the results from Algorithm 2; it shows when each link was added to the solution (first 100km, second 100km, etc). We can see that, generally, road segments around cycling infrastructure are prioritized, except for those neighboring cycling infrastructure on the very periphery. The first 100km is also spatially distributed across the city, with no apparent bias towards a particular area.

It is also important to understand how the different highway types contribute to the proposed network. Figure \@ref(fig:growth3MapandBar) shows that most of the flow will be on residential and tertiary roads, as expected from the weighting profile defined in Table **reference the table**.

```{r growth3MapandBar, fig.cap="Results of Alg. 2 (Manchester)", out.width="45%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_priority_all_FLOW.png",
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_investment_highways_flow.png"
))
```

@@

Existing cycling infrastructure is made up of many disconnected components. Both Algorithm 1 and 2 start with all existing segregated cycling infrastructure and aim to create an efficient, connected network. Figure \@ref(fig:componentsandGCC) shows that both algorithms gradually reduce the number of components as more infrastructure is added, but Algorithm 2 is able to provide better connectivity with less investment.

Consistent growth can also be seen for the size of the Largest Connected Component in the proposed bicycle network (Figure \@ref(fig:componentsandGCC)). Here however, we find that there is little difference between both Algorithms.

```{r componentsandGCC, fig.cap="Network Characteristics", out.width="45%", fig.show='hold', echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_util_egal_components_number_comparisonManchester.png",
  "data/Manchester/Plots/Growth_Results/growth_util_egal_components_gcc_comparisonManchester.png"
))
```
